Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-04-07 TABLE/magnifications.tex
Incorporated comments from KS, MJ, AZ   * added positions   * added a section on cosmological parameter uncertainty   * subsumed the section 3.3 discussion into the preceding subsection

Sharon(v1)   & 2.53     & 2.57  &   2.41$-$2.75 & \citealt{Jullo:2007}  & LENSTOOL parametric, strong-lensing based model\\

@@

CATS-SL      & 2.25     & 2.27  &   2.23$-$2.32 &   \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL parametric strong-lensing based model.\\
CATS-SL+WL   & \nodata  & 2.62  &   2.44$-$2.80 & \citealt{Jullo:2009,Jauzac:2012} &  LENSTOOL parametric model with both strong and weak lensing constraints.\\
Jauzac		 & \nodata  & 3.37  &   3.22$-$3.51 &   \citealt{Jauzac:2014,Richard:2014} & Updated version of the CATS-SL model, adds 33 new multiply-imaged galaxies.\\
GLAFIC       & 2.32     & 2.28  &   2.17$-$2.35 &   \citealt{Oguri:2010,Ishigaki:2015} & Parametric strong-lensing model using the {\tt GLAFIC} code.\tablenotemark{d} \\
Zitrin-NFW   & 2.07     & 2.27  &   2.05$-$2.50 &   \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD\tablenotemark{e} profiles for galaxies and NFW\tablenotemark{f} profiles for dark matter halos.\\

@@

Williams     & 2.67     & 2.78  &   1.64$-$5.46 &   \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} & {\tt GRALE}\tablenotemark{g} : Free-form strong-lensing model using a genetic algorithm.  \\
Merten       & 2.31     & 2.22  &   2.03$-$2.89 &   \citealt{Merten:2009,Merten:2011} &  {\tt SaWLENS},\tablenotemark{h} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
Lam			 & \nodata  & 2.77  &   2.41$-$3.13 &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{h} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
Diego\tablenotemark{i}        & \nodata  & 2.10  &   1.74$-$2.46 &   \citealt{Sendra:2014,Lam:2014} & \change{Alternative implementation of the {\tt WSLAP+}\tablenotemark{h} model, using a different set of strong-lensing constraints and redshifts.}

@@

\tablenotetext{d}{{\tt GLAFIC} : \url{http://www.slac.stanford.edu/~oguri/glafic/}}
\tablenotetext{e}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
\tablenotetext{f}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
\tablenotetext{g}{{\tt GRALE} : GRAvitational LEnsing.}
\tablenotetext{h}{{\tt SaWLENS} : Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
\tablenotetext{h}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies \change{(Note: no weak-lensing constraints used for Abell 2744)}}
\tablenotetext{i}{\change{No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the closely related Lam model.}}

>>>>

Sharon(v1)   & 2.53     & 2.57  &   2.41$-$2.75 & \citealt{Jullo:2007}  & LENSTOOL\tablenotemark{c} parametric, strong-lensing based model\\

@@

CATS-SL      & 2.25     & 2.27  &   2.23$-$2.32 &   \citealt{Jullo:2007,Richard:2014} &  CATS\tablenotemark{d} team implementation of LENSTOOL parametric strong-lensing based model.\\
CATS-SL+WL   & \nodata  & 2.62  &   2.44$-$2.80 &   \citealt{Jullo:2007,Richard:2014} &  CATS team LENSTOOL parametric model with both strong and weak lensing constraints.\\
CATS-SL(v2)  & 3.37     & 3.35  &   3.18$-$3.53 &   \citealt{Richard:2014,Jauzac:2014} & Updated version of the CATS-SL model, adds 33 new multiply-imaged galaxies.\\
GLAFIC       & 2.32     & 2.28  &   2.17$-$2.35 &   \citealt{Oguri:2010,Ishigaki:2015} & Parametric strong-lensing model using the {\tt GLAFIC} code.\tablenotemark{e} \\
Zitrin-NFW   & 2.07     & 2.27  &   2.05$-$2.50 &   \citealt{Zitrin:2013a} &  Parametric strong-lensing model using PIEMD\tablenotemark{f} profiles for galaxies and NFW\tablenotemark{g} profiles for dark matter halos.\\

@@

Williams     & 2.67     & 2.78  &   1.64$-$5.46 &   \citealt{Liesenborgs:2006,Liesenborgs:2007,Mohammed:2014} & {\tt GRALE}\tablenotemark{h} : Free-form strong-lensing model using a genetic algorithm.  \\
Merten       & 2.31     & 2.22  &   2.03$-$2.89 &   \citealt{Merten:2009,Merten:2011} &  {\tt SaWLENS},\tablenotemark{i} Grid-based free-form strong+weak lensing based model using adaptive mesh refinement.\\
Lam			 & \nodata  & 2.77  &   2.41$-$3.13 &   \citealt{Sendra:2014,Lam:2014} & {\tt WSLAP+}\tablenotemark{j} : Free-form model strong-lensing using a grid-based method, supplemented by deflections fixed to cluster member galaxies.\\
Diego\tablenotemark{k}   & \nodata  & 2.10  &   1.74$-$2.46 &   \citealt{Sendra:2014,Lam:2014} & Alternative implementation of the {\tt WSLAP+}\tablenotemark{j} model, using a different set of strong-lensing constraints and redshifts.

@@

\tablenotetext{d}{{\tt CATS} : Clusters As TelescopeS lens modeling team.}
\tablenotetext{e}{{\tt GLAFIC} : \url{http://www.slac.stanford.edu/~oguri/glafic/}}
\tablenotetext{f}{PIEMD: Pseudo Isothermal Elliptical Mass Distrubition}
\tablenotetext{g}{NFW : Navarro-Frenk-White mass density profile \citep{Navarro:1997}.}
\tablenotetext{h}{{\tt GRALE} : GRAvitational LEnsing.}
\tablenotetext{i}{{\tt SaWLENS} : Strong and Weak LENSing analysis code. \url{http://www.julianmerten.net/codes.html}}
\tablenotetext{j}{{\tt WSLAP+} : Weak and Strong Lensing Analysis Package plus member galaxies \change{(Note: no weak-lensing constraints used for Abell 2744)}}
\tablenotetext{k}{No uncertainty estimates were available for the Diego implementation of the {\tt WSLAP+} model, so we adopt the uncertainties from the closely related Lam model.}

### 2015-04-07 snTomas.tex
Incorporated comments from KS, MJ, AZ   * added positions   * added a section on cosmological parameter uncertainty   * subsumed the section 3.3 discussion into the preceding subsection

\changeG{
Galaxy clusters can be used as cosmic telescopes to magnify distant
background objects through gravitational lensing, which can
substantially increase the reach of deep imaging surveys.  The lensing
magnification enables the study of objects that would otherwise be
unobservable because they are either intrinsically
faint \citep[e.g.][]{Schenker:2012,Alavi:2014} or extremely
distant \citep[e.g.][]{Franx:1997,Ellis:2001,Hu:2002,Kneib:2004,Richard:2006,Richard:2008,Bouwens:2009a,Maizy:2010,Zheng:2012,Coe:2013,Bouwens:2014,Zitrin:2014}.
Background galaxies are also {\it spatially} magnified, allowing for
studies of the internal structure of galaxies in the early universe
with resolutions of $\sim$100
pc \citep[e.g.]{Stark:2008,Jones:2010,Yuan:2011,Livermore:2015}.
}

@@

SN \tomas\ was discovered in Hubble Space Telescop (\HST) observations
with the Advanced Camera for Surveys (ACS) in the F606W and F814W
bands (V and i), collected on UT 2014 May 15 as part of the Hubble
Frontier Fields (HFF) survey (PI:J.Lotz,
HST-PID:13495).\footnote{\url{http://www.stsci.edu/hst/campaigns/frontier-fields}}
The HFF program is a 3-year director's discretionary initiative that
is collecting 140 orbits of HST imaging (roughly 340 ksec) on six
massive galaxy clusters, plus 6 accompanying parallel fields.
Each field is observed in 3 optical bands (ACS F435W, F606W and F814W)
and 4 infrared (IR) bands (WFC3-IR F105W, F125W, F140W, and F160W),
although the optical and IR imaging campaigns are separated by $\sim$6
months. Abell 2744 was the first cluster observed, with IR imaging
spanning 2013 October-November, and optical imaging from 2014
May-July.  A composite image of the HFF data showing the SN is
presented in Figure~\ref{fig:DiscoveryImage}.  The SN detection was
made in difference images constructed using template imaging of Abell
2744 from HST+ACS observations taken in 2009 (PI:Dupke,
HST-PID:11689).

@@

\subsection{Comparison to Model Predictions}
\label{sec:ComparisonToModelPredictions}

@@

The line of sight to SN \tomas\ is 5\farcs8 from a bright cluster
member galaxy, due North of the SN position (see
Figure~\ref{fig:DiscoveryImage}).  If the mass-to-light ratio (M/L)
for this galaxy were significantly different from the M/L for other
cluster member galaxies, then its proximity to the SN sight-line could
introduce a bias in the magnification.  This bias might be
particularly acute for models that make a strict ``light traces mass''
assumption, such as the Sharon, CATS, Jauzac, GLAFIC and Zitrin-LTM
models.

We tested this hypothesis using the Jauzac model by allowing the mass
of the nearby cluster member galaxy to vary as a free parameter in the
model. We found that the change in the SN \tomas\ magnification
prediction was less than $\Delta\mu=0.1$.  This additional dispersion
is already included in the uncertainties quoted for that model in
Table~\ref{tab:PredictedMagnifications} and
Figure~\ref{fig:lensingtest}.  Furthermore, an erroneous M/L
value for the nearby cluster member galaxy could not explain the
systematic shift of all lens models, because some do not incorporate
cluster member galaxies into their constraints at all (the free-form
Bradac, Williams and Merten models).

@@

At the outset of the HFF survey, only 33 multiply-imaged galaxies
behind Abell 2744 were known.  One might expect that the addition of
new lensing constraints from the HFF data would improve the model
constraints and reduce the tension between the predicted and observed
magnification.  However, for \changeG{two} of the most recent
models \citep{Jauzac:2014c,Lam:2014} that include new strong-lensing
constraints, the predicted magnification is still significantly higher
than the observed value.  Again the CATS model family provides a
useful case study.  The Jauzac model shares the same lens modeling
software (LensTool), and the same primary methodology as the earlier
CATS models.  A key difference is that the Jauzac model incorporates
many new multiply imaged galaxies and corrects a mis-identified
multiply-imaged system near the SN \tomas\ position.  These
improvements should in principle make the Jauzac model magnification
estimates more accurate, though we in fact see the opposite result:
the Jauzac model predicts a $\mu$ that is higher than the measured
value by \changeG{$4.3\sigma$.}

This shift to higher magnifications is not, however, unique to the
SN \tomas\ position.  \citet{Jauzac:2014c} noted that their updated
mass model of Abell 2744 results in a systematic increase in the
magnification values across the cluster field. Examining a sample of
$\sim$30 multiple images, \citeauthor{Jauzac:2014c} found that the
magnifications increased by a factor of $\sim1.5$ relative to pre-HFF
models.  Although this single sight-line can only provide a very
limited test of the model, the \changeG{$4.3\sigma$} discrepancy is at
least a strong suggestion that \changeR{even with a large number of
high-quality} strong-lensing constraints \changeR{it is still possible
to generate} magnification maps that are susceptible to systematic
biases.

\change{
\subsection{Misidentification of System 3}
\label{sec:MisidentificationOfSystem3}
}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/system3.png}
\caption{ 
The disputed component of the multiply-imaged galaxy System 3. The
original position, as given in \citet{Merten:2011} is marked with a
dashed magenta circle labeled 3.3. The solid magenta circle shows the
revised location as proposed in \citet{Jauzac:2014c}.  Both positions
are $\sim$10\arcsec\ from the SN location.  The inset panel shows the
other two components of this multiply-imaged system, 3.1 and 3.2 (on
the same scale as the main panel), which are located north-east of the
cluster center.
\label{fig:system3} }
\end{center}
\end{figure}

\change{
It is important to note that in regards to the impact on this
particular sight-line, not all strong-lensing constraints are equal.
An error in the association of multiple images or in the redshift of a
multiply-imaged galaxy would have a more significant impact if that
system has a projected position close to our SN
sight-line \changeG{\citep[see][for a quantitative assessment of this
effect]{Johnson:2014}.}  It happens that there is one such system, for
which the position of a multiple image near SN \tomas\ is presently
disputed.  }

\change{
This multiply-imaged galaxy was originally labeled as {\it System 3}
in \citet{Merten:2011}.  As shown in Figure~\ref{fig:system3}, it is
stretched into two adjacent arcs northeast of the cluster core (images
3.1 and 3.2), with a third image on the western edge of the
strong-lensing region (image 3.3 at 00:14:18.595,
-30:23:58.42).  \citet{Richard:2014} echoed this initial
identification in producing the {\tt CATS} models, which we cite in
Table~\ref{tab:PredictedMagnifications} and
Figure~\ref{fig:lensingtest}.  In developing the {\tt Sharon-v2}
models, \citet{Johnson:2014} provided a secure spectroscopic
constraint of $z=3.98\pm0.02$ for this system, based on a spectrum of
the combined 3.1+3.2 source. The identification of the original image
3.3 has been called into question by two independent analyses.  Using
HFF imaging data, \citet{Lam:2014} suggested an alternative third
image for this system roughly 8\arcsec\ to the south, which we will
call \33p\ (00:14:18.39, -30:24:06.53).
However, \citeauthor{Lam:2014} rejected this possibility based on a
difference in colors between \33p\ and images 3.1 and 3.2.  In
contrast, \citeauthor{Jauzac:2014c} argue that the position \33p\
is correct, and find that reassigning this multiple image results in a
tighter model reconstruction for the locations of other
multiply-imaged systems in the vicinity.
}

\change{
Resolving the identification of this single multiply-imaged galaxy
could be a component in resolving the magnification
discrepancy, though it is unlikely to completely remove the tension.
It is true that the model that reassigns the position to \33p\
({\tt Jauzac}) is also the one with the largest deviation from our
observed $\mu$ value.  However, \citet{Jauzac:2014c} have already
evaluated the impact of relocating this single source, and
they find that it is not responsible for the observed increase in
magnifications across the field. Rather, the 
primary cause for the general magnification increase is the addition
of new multiple images in the Northern region, detected using the new
HFF data. }

@@

@@

Taking advantage of the availability of eleven well-constrained lens
models for the Abell 2744 cluster, we have used SN \tomas\ to ask
how accurately these lens models can predict the magnification along
this line of sight.   We find that these models are consistent, and
fairly accurate, collectively predicting $\mu=2.60\pm0.34$.  This is
encouraging, and reinforces the quality and value of these public lens
models for studying magnified background objects.   However, the fact
that all models predict a larger magnification value than we observe
is an indication that there is a small systematic bias inherent to
this cluster or sight-line.

We have speculated on the origin of this systematic bias,
evaluating six possible causes:

\begin{enumerate}
\item The close proximity of a cluster member galaxy is leading to a
biased magnification, because that galaxy's M/L is atypical.
\item The models are limited by a scarcity of strong lensing constraints
\item The cluster mass profile exhibits a sudden change outside of the core
strong-lensing region, where we lack multiply-imaged background
sources to constrain it. 
\item \change{The redshift assigned to SN \tomas\ is in error.}
\item \change{SN \tomas\ is dimmed by foreground dust.}
\item \change{SN \tomas\ is not a normal Type Ia SN.}
\end{enumerate}

\noindent The first three of these take on the discrepancy from 
the lens modeling side, but none are completely satisfactory. For each
of these scenarios, we would expect that certain subsets of the
available lens models would be less sensitive to the proposed
systematic bias.  However, the small discrepancy between the predicted
and observed lensing magnification is persistent when we bifurcate the
sample of lens models according to methodology (parametric
vs. free-form), number of strong-lensing constraints (pre- vs
post-HFF), and scope of lensing constraints (strong-lensing only
vs. strong+weak). Thus, comparison of the available models does not
provide any definitive explanation for this magnification tension.

>>>>

\changeG{
Galaxy clusters can be used as cosmic telescopes to magnify distant
background objects through gravitational lensing, which can
substantially increase the reach of deep imaging surveys.  The lensing
magnification enables the study of objects that would otherwise be
unobservable because they are either intrinsically
faint \citep[e.g.][]{Schenker:2012,Alavi:2014} or extremely
distant \citep[e.g.][]{Franx:1997,Ellis:2001,Hu:2002,Kneib:2004,Richard:2006,Richard:2008,Bouwens:2009a,Maizy:2010,Zheng:2012,Coe:2013,Bouwens:2014,Zitrin:2014b}.
Background galaxies are also {\it spatially} magnified, allowing for
studies of the internal structure of galaxies in the early universe
with resolutions of $\sim$100
pc \citep[e.g.]{Stark:2008,Jones:2010,Yuan:2011,Livermore:2015}.
}

@@

SN \tomas\ was discovered in Hubble Space Telescop (\HST) observations
with the Advanced Camera for Surveys (ACS) in the F606W and F814W
bands (V and i), collected on UT 2014 May 15 as part of the Hubble
Frontier Fields (HFF) survey (PI:J.Lotz,
HST-PID:13495).\footnote{\url{http://www.stsci.edu/hst/campaigns/frontier-fields}}
The HFF program is a 3-year director's discretionary initiative that
is collecting 140 orbits of HST imaging (roughly 340 ksec) on six
massive galaxy clusters, plus 6 accompanying parallel fields.  Each
field is observed in 3 optical bands (ACS F435W, F606W and F814W) and
4 infrared (IR) bands (WFC3-IR F105W, F125W, F140W, and F160W),
although the optical and IR imaging campaigns are separated by $\sim$6
months. Abell 2744 was the first cluster observed, with IR imaging
spanning 2013 October-November, and optical imaging from 2014
May-July.  A composite image of the HFF data showing the SN is
presented in Figure~\ref{fig:DiscoveryImage}, \changeR{and the
locations of the cluster center, the SN, and the presumed host galaxy
are given in Table~\ref{tab:Positions}.}  The SN detection was made in
difference images constructed using template imaging of Abell 2744
from HST+ACS observations taken in 2009 (PI:Dupke, HST-PID:11689).

\input{TABLE/positions}

@@

%\subsection{Comparison to Model Predictions}
%\label{sec:ComparisonToModelPredictions}

@@

The line of sight to SN \tomas\ is 5\farcs8 from a bright cluster
member galaxy, due North of the SN position (see
Figure~\ref{fig:DiscoveryImage}).  If the mass-to-light ratio (M/L)
for this galaxy were significantly different from the M/L for other
cluster member galaxies, then its proximity to the SN sight-line could
introduce a bias in the magnification.  This bias might be
particularly acute for models that \changeR{hew more closely to a
simple} ``light traces mass'' assumption, such as the Sharon, CATS,
GLAFIC and Zitrin-LTM models.

We tested this hypothesis using the CATS-SL(v2) model by allowing the mass
of the nearby cluster member galaxy to vary as a free parameter in the
model. We found that the change in the SN \tomas\ magnification
prediction was less than $\Delta\mu=0.1$.  This additional dispersion
is already included in the uncertainties quoted for that model in
Table~\ref{tab:PredictedMagnifications} and
Figure~\ref{fig:lensingtest}.  Furthermore, an erroneous M/L
value for the nearby cluster member galaxy could not explain the
systematic shift of all lens models, because some do not incorporate
cluster member galaxies into their constraints at all (the free-form
Bradac, Williams and Merten models).

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/system3.png}
\caption{ 
The disputed component of the multiply-imaged galaxy System 3. The
original position, as given in \citet{Merten:2011} is marked with a
dashed magenta circle labeled 3.3. The solid magenta circle
labeled \33p\ shows the revised location as proposed
in \citet{Jauzac:2014c}.  Both positions are $\sim$10\arcsec\ from the
SN location.  The inset panel shows the other two components of this
multiply-imaged system, 3.1 and 3.2 (on the same scale as the main
panel), which are located north-east of the cluster center, and have a
secure spectroscopic redshift of $z=3.98\pm0.02$ \citep{Johnson:2014}.
\label{fig:system3} }
\end{center}
\end{figure}

At the outset of the HFF survey, only 33 multiply-imaged galaxies
behind Abell 2744 were known.  One might expect that the addition of
new lensing constraints from the HFF data would improve the model
constraints and reduce the tension between the predicted and observed
magnification.  However, for \changeG{two} of the most recent
models \citep{Jauzac:2014c,Lam:2014} that include new strong-lensing
constraints, the predicted magnification is still significantly higher
than the observed value.  Again the CATS model family provides a
useful case study.  The CATS-SL(v2) model \citep[from][]{Jauzac:2014c}
shares the same lens modeling software (LensTool), and the same
primary methodology as the earlier CATS models, \changeR{though with
two key differences:  (1) the CATS-SL(v2) model changes the location of a
multiply-imaged system near the SN \tomas\ position; and (2) the model
incorporates 33 new multiply imaged galaxies.}  These improvements
should in principle make the CATS-SL(v2) model magnification estimates
more accurate, though we in fact see the opposite result: the
CATS-SL(v2) model predicts a $\mu$ that is higher than the measured
value by \changeR{$4.1\sigma$, and higher than either of the previous
two versions of the CATS models.}

\changeR{
The change in location proposed by \citet{Jauzac:2014c} is for image
3.3, the third component of a triply-imaged
galaxy \citep{Merten:2011}, shown in Figure~\ref{fig:system3}.  Images
3.1 and 3.2 of this system have a secure spectroscopic redshift of
$z=3.98\pm0.02$ \citep{Johnson:2014}. \citet{Jauzac:2014c} found that
reassigning this multiple image to a source roughly 8\arcsec\ to the
south results in a tighter model reconstruction for the locations of
other multiply-imaged systems in the vicinity \citep[though][argue
against the reassignment based on the colors of the two sources in
question]{Lam:2014}.  Given the large discrepancy between the
CATS-SL(v2) model and the SN measurement, one might question whether
this change in the position of image 3.3 is driving the increase in
the predicted $\mu$ for SN \tomas. However, \citet{Jauzac:2014c} also
examined a version of the CATS-SL(v2) model where this single source
is left in the original position, and find that it does not
significantly affect the predicted magnification.}

\changeR{Furthermore,} the shift to higher magnifications is not unique to the
SN \tomas\ position.  \citet{Jauzac:2014c} noted that their updated
mass model of Abell 2744 results in a systematic increase in the
magnification values across the cluster field. Examining a sample of
$\sim$30 multiple images, \citeauthor{Jauzac:2014c} found that the
magnifications increased by a factor of $\sim1.5$ relative to pre-HFF
models.  Although \changeR{the single sight-line to SN \tomas\ } can
only provide a very limited test of the model,
the \changeR{$4.1\sigma$} discrepancy is at least a strong suggestion
that \changeR{even with a large number of high-quality} strong-lensing
constraints \changeR{it is still possible to generate} magnification
maps that are susceptible to systematic biases.

@@

\subsection{Cosmological Uncertainty}

\changeR{
All of the models presented here use a fixed assumption for the
parameters of a standard \LCDM\ cosmology (typically: \Om=0.3,\OL=0.7,\Ho=70 km
s$^{-1}$ Mpc$^{-1}$).  The parameter values selected for this fiducial
cosmology do have an impact on the inferred magnifications, and
variation of these parameters must be accounted for when using cluster
mass models for cosmological tests \citep{Zitrin:2014b}. 
\citep{Bayliss:2015} demonstrated that
changing the cosmological parameter within the range of current
acceptable cosmologies \citep[e.g.][]{Hinshaw:2013,Planck:2015},
introduces a magnification uncertainty that is comparable in magnitude
to that of the statistical uncertainties.  This leads to the
conclusion that the lens modeling uncertainties presented here are
underestimated, and should be significantly increased. 
}

\changeR{
As a quantitative example, we have modified the Sharon(v2) model to
include this cosmological parameter uncertainty,
following \citep{Bayliss:2015}. At the position of SN \tomas, the
68\%\ confidence range for the magnification at $z=1.31$ increases
from [2.63,2.83] to [2.42,2.85], and the best-fit magnification value
of $mu=2.73$ remains the same.  This moves the Sharon(v2) model from
being discrepant at the $2.5\sigma$ level to a $1.75\sigma$ tension.
Incorporating this cosmological parameter uncertainty in the other
models would similarly reduce the tension between models and
observation, but would not resolve the overall systematic shift.  Even
a factor of 2.5 increase in the uncertainties (the most drastic change
seen in the analysis of \citep{Bayliss:2015}) would still leave the
most extreme outlier (CATS-SL(v2)) discrepant by $2.6\sigma$.
}

@@

Taking advantage of the availability of \changeR{14} well-constrained lens
models for the Abell 2744 cluster, we have used SN \tomas\ to ask
how accurately these lens models can predict the magnification along
this line of sight.   We find that these models are consistent, and
fairly accurate, collectively predicting $\mu=2.60\pm0.34$.  This is
encouraging, and reinforces the quality and value of these public lens
models for studying magnified background objects.   However, the fact
that all models predict a larger magnification value than we observe
is an indication that there is a small systematic bias inherent to
this cluster or sight-line.

We have speculated on the origin of this systematic bias,
evaluating \changeR{seven} possible causes:

\begin{enumerate}
\item The close proximity of a cluster member galaxy is leading to a
biased magnification, because that galaxy's M/L is atypical.
\item The models are limited by a scarcity of strong lensing constraints
\item Model uncertainties are underestimated, by not accounting for 
       uncertainties in cosmological parameters.
\item The cluster mass profile exhibits a sudden change outside of the core
strong-lensing region, where we lack multiply-imaged background
sources to constrain it.
\item \change{The redshift assigned to SN \tomas\ is in error.}
\item \change{SN \tomas\ is dimmed by foreground dust.}
\item \change{SN \tomas\ is not a normal Type Ia SN.}
\end{enumerate}

\noindent The first \changeR{four} of these take on the discrepancy from 
the lens modeling side, but none are completely satisfactory. For each
of these scenarios, we would expect that certain subsets of the
available lens models would be less sensitive to the proposed
systematic bias.  However, the small discrepancy between the predicted
and observed lensing magnification is persistent when we bifurcate the
sample of lens models according to methodology (parametric
vs. free-form), number of strong-lensing constraints (pre- vs
post-HFF), and scope of lensing constraints (strong-lensing only
vs. strong+weak). Thus, comparison of the available models does not
provide any definitive explanation for this magnification tension.
